Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
push some minor changes

\newif\ifdraft\drafttrue  % set true to show comments
%\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

In this evaluation, we aim to answer four primary questions:
\begin{enumerate}
\item Can the algorithm (with suitable examples and termination
  tuning) find the correct lens?
\item Is the synthesis procedure efficient enough to be used in everyday
  development?
\item How much slower is our tool on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses?
\item How much termination tuning is necessary and how does the heuristic affect the
  results?
\end{enumerate}

@@

To determine whether the system can synthesize the desired lenses, we ran the
symmetric synthesis algorithm interactively on all 48 tasks,
working with the system to create sufficient examples and adjust the termination
tuning.  In all cases, the desired lens was obtained, which we verified by
manually inspecting the generated lens programs.
%
The majority of the tasks required only a single example and none required
more than three examples in order to synthesize the desired lens.\footnote{In
  one benchmark, we supplied a fourth example that was later discovered to 
  be unnecessary.}

Adjusting the tuning parameter was needed in only 9 of the 48 tasks. In practice, we
found that customizing the termination metric to be quite easy: if manual
inspection of the lens showed there were too few bijections, we would increase
the termination parameter. If synthesis took too long, we would decrease it.
Section~\ref{subsec:effect-of-heuristics}, studies the effect of fixing the
termination metric.

>>>>

\newif\ifdraft\draftfalse  % set true to show comments
%\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

In this evaluation, we aim to answer four primary questions:
\begin{enumerate}
\item Can the algorithm (with suitable examples and termination
  tuning) find the correct lens?
\item Is the synthesis procedure efficient enough to be used in everyday
  development?
\item How much slower is our tool on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses?
\item How effective is the information-theoretic search heuristic and how does
  termination tuning affect the results?
\end{enumerate}

@@

To determine whether the system can synthesize the desired lenses, we ran the
symmetric synthesis algorithm interactively on all 48 tasks,
working with the system to create sufficient examples and adjust the termination
parameter.  In all cases, the desired lens was obtained, which we verified by
manually inspecting the generated lens programs.
%
The majority of the tasks required only a single example and none required
more than three examples in order to synthesize the desired lens.\footnote{In
  one benchmark, we supplied a fourth example that was later discovered to 
  be unnecessary.}

Adjusting the termination parameter was needed in only 9 of the 48 tasks. In practice, we
found that customizing the termination metric to be quite easy: if manual
inspection of the lens showed there were too few bijections, we would increase
the termination parameter. If synthesis took too long, we would decrease it.
Section~\ref{subsec:effect-of-heuristics}, studies the effect of fixing the
termination metric.
